Linear and modal analysis applying the FE$^2$ multi-scale method for composite materials.

### 2018-02-08 article.tex
adding micro-problem implementation section writing unknowns elimination method for periodic boundary conditions
authors in 1 line

\documentclass[review]{elsarticle}

@@

%% Group authors per affiliation:
%\author{Elsevier\fnref{myfootnote}}
%\address{Radarweg 29, Amsterdam}
%\fntext[myfootnote]{Since 1880.}
\author{Guido Giuntoli\fnref{myfootnote}}
\address{Carrer Jordi Girona 29, Barcelona}
\author{Mariano V\'azquez\fnref{myfootnote}}
\address{Carrer Jordi Girona 29, Barcelona}
\author{Sergio Oller\fnref{myfootnote}}
\address{Carrer Jordi Girona 29, Barcelona}

\fntext[myfootnote]{\ead[url]{guido.bsc.elisya.org}}

@@

\linenumbers

@@

>>>>

\documentclass[3p]{elsarticle}
%\documentclass[review]{elsarticle}

@@

%% Group authors per affiliation:
%\author{Elsevier\fnref{myfootnote}}
%\address{Radarweg 29, Amsterdam}
%\fntext[myfootnote]{Since 1880.}
\author[bsc]{Guido Giuntoli}
%\address{Carrer Jordi Girona 29, Barcelona}
\author[bsc]{Mariano V\'azquez}
%\address{Carrer Jordi Girona 29, Barcelona}
\author[upc]{Sergio Oller}
%\address{Carrer Jordi Girona 29, Barcelona}
\address[bsc]{River Valley Technologies, SJP Building, Cotton Hills, Trivandrum, Kerala, India 695014}
\address[upc]{River Valley Technologies, SJP Building, Cotton Hills, Trivandrum, Kerala, India 695014}

%\fntext[myfootnote]{\ead[url]{guido.bsc.elisya.org}}

@@

%\linenumbers

@@

\section{Numerical Implementation of the Micro-problem}

\subsection{Uniform Strains Boundary Conditions}

\subsection{Periodic Boundary Conditions}

\begin{equation}
\left\{
\begin{array}{ll}
\bm{f}_a(\bm{u}) = \bm{0} \\
\bm{f}_b^+(\bm{u}) + \bm{f}_b^-(\bm{u}) = \bm{0} \\
\bm{u}^+ - \bm{u}^- - \overline{\bm{\epsilon}} ( \bm{x}^+ - \bm{x}^- ) = \bm{0}\\
\end{array}
\right.
\end{equation}

\begin{equation}
\bm{c}(\bm{x}) = \overline{\bm{\epsilon}} ( \bm{x}^+ - \bm{x}^- ) \\
\end{equation}

\begin{equation}
\bm{u}^+ - \bm{u}^- - \bm{c}(\bm{x}) = \bm{0}
\end{equation}

\subsubsection{The Unknowns Elimination Method}

\begin{equation}
\bm{u}^+ = \bm{u}^- + \bm{c}(\bm{x}) 
\end{equation}

\begin{equation}
\bm{u} = \begin{bmatrix}\bm{u}_a & \bm{u}_+ & \bm{u}_-\end{bmatrix}^T
\end{equation}

\begin{equation}
d\bm{u}^+ = d\bm{u}^-
\end{equation}

\begin{equation}
d\bm{u} = \begin{bmatrix}d\bm{u}_a & d\bm{u}_+ & d\bm{u}_-\end{bmatrix}^T = \begin{bmatrix}d\bm{u}_a & d\bm{u}_- & d\bm{u}_-\end{bmatrix}^T
\end{equation}

\begin{equation}
\begin{bmatrix}
\frac{\bm{f}_a}{d\bm{u}_a} & \frac{\bm{f}_a}{d\bm{u}_+} & \frac{\bm{f}_a}{d\bm{u}_-}\\
\frac{\bm{f}_b^+ + \bm{f}_b^-}{d\bm{u}_a} & \frac{\bm{f}_b^+ + \bm{f}_b^-}{d\bm{u}_+} & \frac{\bm{f}_b^+ + \bm{f}_b^-}{d\bm{u}_-}\\
\end{bmatrix}
\cdot
\begin{bmatrix}d\bm{u}_a \\ d\bm{u}_- \\ d\bm{u}_-\end{bmatrix}
=
\begin{bmatrix}\bm{f}_a(\bm{u}^{k-1}) \\ \bm{f}_b^+(\bm{u}^{k-1}) + \bm{f}_b^-(\bm{u}^{k-1}) \end{bmatrix}
\end{equation}

\begin{equation}
\begin{bmatrix}
K_{aa}          & K_{a+} + K_{a-} \\
K_{+a} + K_{-a} & K_{++} + K_{-+}  + K_{+-} + K_{--} \\
\end{bmatrix}
\cdot
\begin{bmatrix}d\bm{u}_a \\ d\bm{u}_- \end{bmatrix}
=
-\begin{bmatrix}\bm{f}_a(\bm{u}^{k-1}) \\ \bm{f}_b^+(\bm{u}^{k-1}) + \bm{f}_b^-(\bm{u}^{k-1}) \end{bmatrix}
\end{equation}

The algorithm:

\begin{equation}
\bm{u}^{i=0} = \begin{bmatrix}\bm{u}_a^{0} \\ \bm{u}_+^{0} \\ \bm{u}_-^{0}\end{bmatrix} = \begin{bmatrix}\bm{0} \\ \bm{c} \\ \bm{0}\end{bmatrix}
\end{equation}

\begin{equation}
\bm{u}_a^{0} = \bm{0}, \, \bm{u}_-^{0} = 0 \text{ and } \bm{u}_+^{0} = \bm{u}_-^{0} + \bm{c} = \bm{c}
\end{equation}

\begin{equation}
\bm{J}^{i-1}\cdot d\bm{u}^{i}
=
-r(\bm{u}^{i-1})
\end{equation}

\begin{equation}
\bm{u}^{i+1} = 
\begin{bmatrix}\bm{u}_a^{i-1} \\ \bm{u}_+^{i-1} \\ \bm{u}_-^{i-1}\end{bmatrix} 
+ 
\begin{bmatrix} d\bm{u}_a^{i} \\ d\bm{u}_+^{i} \\ d\bm{u}_-^{i}\end{bmatrix}
\end{equation}

\subsubsection{The Lagrange Multipliers Method}

\subsection{Uniform Stresses Boundary Conditions}
